### 2014-08-06 analysis/figures/paper_figures.tex
Resting state for rabbit 9

\raisebox{-0.5\height}{\rotatebox{90}{Resting State (SSAEP)}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_15_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_24_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_33_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_36_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_12_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssaep_40_40-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{Resting State (SSVEP)}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_11_38-crop.pdf}} & % basilar tip
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_23_38-crop.pdf}} & % mid-basilar
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_32_38-crop.pdf}} & % vb junction
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_35_38-crop.pdf}} & % basilar tip
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_14_38-crop.pdf}} & % live control
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/10rabbit_may_15_2014_ssvep_38_38-crop.pdf}} \\ % dead control

@@

>>>>

@@

%\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD 9 (SSAEP)}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_8_8_not_subtracted-crop.pdf}} & % basilar tip
%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_32_8_not_subtracted-crop.pdf}} & % mid-basilar
%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_35_8_not_subtracted-crop.pdf}} & % vb junction
%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_41_8_not_subtracted-crop.pdf}} & % basilar tip
%\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssaep_11_8_not_subtracted-crop.pdf}} & % live control
%\\
\raisebox{-0.5\height}{\rotatebox{90}{Resting PSD 9 (SSVEP)}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_5_5_not_subtracted-crop.pdf}} & % basilar tip
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_29_5_not_subtracted-crop.pdf}} & % mid-basilar
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_32_5_not_subtracted-crop.pdf}} & % vb junction
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_38_5_not_subtracted-crop.pdf}} & % basilar tip
\raisebox{-0.5\height}{\includegraphics[scale=0.08]{../ssavep/matlab_data/9rabbit_may_6_2014_ssvep_8_5_not_subtracted-crop.pdf}} & % live control
\\
